### 2011-08-29 resume_cv/cv.tex
Updated my cv

\section{Contact Information}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{1.85in}%
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
795 Walnut Avenue & \textit{Cell:} (801) 995-9460 \\
Provo, UT 84604 USA    & \textit{E-mail:} mjg82@byu.edu \\
\end{tabular}

\section{Research Interests}
%
Natural language processing, latent Dirichlet allocation, topic modeling,
Bayesian machine learning, particle swarm optimization

\section{Education}
%
{\textbf{Brigham Young University}},
Provo, Utah USA
\begin{outerlist}
\item[] M.S.,
		Computer Science, April 2011 (anticipated)
        \begin{innerlist}
		\item Thesis Topic: \emph{Information discovery in large corpora
		  through topic modeling}
        \item Advisor: Professor Kevin Seppi
        \end{innerlist}

@@

\section{Awards}
%
Brigham Young University
\begin{innerlist}
\item National Merit Scholarship, 2004--2010
\item Awarded a research grant from the Office of Research and Creative
  Activities in both 2008 and 2009
\item Inducted into the Phi Kappa Phi Honors Society, 2009
\item Barry M. Goldwater Scholarship Nominee, 2009
\item Claricode Medical Essay Scholarship Finalist, 2009
\end{innerlist}

@@

{\textbf{Brigham Young University}}, Provo, Utah USA
\begin{outerlist}
\item[] \textit{Teaching Assistant}%
	\hfill \textbf{May 2010 to June 2010}
\begin{innerlist}
\item CS 470: Introduction to Artificial Intelligence.  Helped create new
  curriculum for the class, tutored students, and graded homework and reports.
\item CS 677: Bayesian Inference.  Tutored students and graded homework and
  reports.
\end{innerlist}

@@

\section{Professional Experience}
%
\textbf{Google, Inc.},
Irvine, California USA
\begin{outerlist}

@@

\section{Journal Publications}
  \begin{bibsection}
	\item Matthew Gardner, Andrew McNabb, and Kevin Seppi.  A Speculative
	  Approach to Parallelization in Particle Swarm Optimization.
	  Submitted to: \emph{Swarm Intelligence}.
  \end{bibsection}

>>>>

\section{Research Interests}
%
Natural language understanding, latent Dirichlet allocation, topic modeling,
Bayesian machine learning, particle swarm optimization

\section{Education}
%
{\textbf{Brigham Young University}},
Provo, Utah USA
\begin{outerlist}
\item[] M.S.,
		Computer Science, August 2011
        \begin{innerlist}
		\item Thesis Topic: \emph{A Speculative Approach to Parallelization in
		  Particle Swarm Optimization}
        \item Advisor: Professor Kevin Seppi
        \end{innerlist}

@@

\section{Awards}
%
Brigham Young University
\begin{innerlist}
\item Hertz Fellowship Finalist, 2011 (one of 50 in the nation from all of the
  physical sciences)
\item National Merit Scholarship, 2004--2010
\item Awarded a research grant from the Office of Research and Creative
  Activities in both 2008 and 2009
\item Inducted into the Phi Kappa Phi Honors Society, 2009
\end{innerlist}

@@

{\textbf{Brigham Young University}}, Provo, Utah USA
\begin{outerlist}

\item[] \textit{Graduate Researcher}%
        \hfill \textbf{May 2010 to May 2011}
\begin{innerlist}
\item Worked in the Applied Machine Learning Lab in the Computer Science
  Department under Dr. Kevin Seppi.
\item Research topics included particle swarm optimization and machine-assisted
  corpus understanding through topic modeling.
\end{innerlist}

\item[] \textit{Teaching Assistant}%
	\hfill \textbf{May 2010 to June 2010}
\begin{innerlist}
\item CS 470: Introduction to Artificial Intelligence.  Helped create new
  curriculum for the class, tutored students, and graded homework and reports.
\item CS 677: Bayesian Inference.  Tutored students and graded homework and
  reports.
\end{innerlist}

@@

\section{Professional Experience}
%
\textbf{Google, Inc.},
Pittsburgh, Pennsylvania, USA
\begin{outerlist}

\item[] \textit{Software Engineering Intern in Product Search}%
        \hfill \textbf{May 2011 to August 2011}
\begin{innerlist}

\item Applied active learning and EVSI techniques to Google's use of Mechanical
  Turk in Product Search.
\end{innerlist}

\textbf{Google, Inc.},
Irvine, California USA
\begin{outerlist}

@@

\section{Journal Publications}
  \begin{bibsection}
	\item Matthew Gardner, Andrew McNabb, and Kevin Seppi.  A Speculative
	  Approach to Parallelization in Particle Swarm Optimization.
	  Accepted at: \emph{Swarm Intelligence} (in press).
  \end{bibsection}
